The Rockerverse: Images, Packages, and Applications for Containerization with R

### 2020-01-23 README.Rmd
add ShinyProxy, update list in README

- `rize`, because discontinued, see #35
- `docker` ([https://bhaskarvk.github.io/docker](https://bhaskarvk.github.io/docker) has been removed from CRAN, seems unmaintained by authors
- https://github.com/svlentink/dockerfiles/blob/master/svlentink/r-base-alpine/Dockerfile because the Alpine image is quite a trivial one
- https://github.com/jlisic/R-docker-centos because CentOS images are also provided by R-hub
- https://github.com/cardcorp/card-rocker because last change 3 years ago, an all based on `rocker/r-base` - lesson learned would be interesting still, see [#15](https://github.com/nuest/rockerverse-paper/issues/15)
- `sevenbridges` includes several Dockerfiles and documentation about using images, and also seems to use Docker in the built workflows but via other tools, not directly, https://sbg.github.io/sevenbridges-r/, https://github.com/sbg/sevenbridges-r/search?p=4&q=docker&unscoped_q=docker
- https://github.com/rocker-jp because it seems to have stalled soon after inception

>>>>

- `rize`, because discontinued, see #35
- `docker` ([https://bhaskarvk.github.io/docker](https://bhaskarvk.github.io/docker) has been removed from CRAN, seems unmaintained by authors
- https://github.com/svlentink/dockerfiles/blob/master/svlentink/r-base-alpine/Dockerfile because the Alpine image is quite a trivial one
- https://github.com/jlisic/R-docker-centos because CentOS images are also provided by R-hub
- `sevenbridges` includes several Dockerfiles and documentation about using images, and also seems to use Docker in the built workflows but via other tools, not directly, https://sbg.github.io/sevenbridges-r/, https://github.com/sbg/sevenbridges-r/search?p=4&q=docker&unscoped_q=docker
- https://github.com/rocker-jp because it seems to have stalled soon after inception
- https://github.com/thomasp85/fiery because no examples/docs for Docker (though probably trivial anyway)
- [RStudio Connect](https://rstudio.com/products/connect/) because while it does use a similar mechanism to seperate processes, it does _not_ use Docker and the comparison would require a lot of background explanation, and not all details are available because the software is proprietary

### 2020-01-23 manuscript.Rmd
add ShinyProxy, update list in README

The cloud is the natural environment of containers, and is the natural mechanism to deploy R server applications.
More and more continuous integration (CI) and continuous delivery (CD) services also use containers, opening up new options for use.
The controlled nature of containers, i.e., the possibility to define the software environment very well, even on remote machines, is crucial here, for example to match test or build environments with production environments.

- `RSelenium`
- [`googleComputeEngineR`](https://cloudyr.github.io/googleComputeEngineR/) (function `gce_vm_template()`)
  - To enable quick deployments of key R services such as RStudio and Shiny onto cloud virtual machines (VMs), this package utilises Dockerfiles to move the labour of setting up those services from the user to a premade Docker image. For example, by specifying the template `template="rstudio"` in `gce_vm_template()/gce_vm()` an up to date RStudio Service image is launched.  Specifying `template="rstudio-gpu"` will launch an RStudio Server image with a GPU attached, etc.  
- [`analogsea`](https://github.com/sckott/analogsea) (digital ocean R client)
- [`plumber`](https://www.rplumber.io/docs/hosting.html#docker)
- [production deployment of neural networks](https://github.com/tmobile/r-tensorflow-api) [@jnolis, @nolistic]
- Kubernetes - A popular platform for managing Docker containers is [Kubernetes](https://kubernetes.io/), which is used for a wide variety of containerized applications. It may be your organisation has a Kubernetes cluster already for other applications. Docker containers are used within Kubernetes clusters to hold native code, for which Kubernetes creates a framework around network connections and scaling of resources up and down. An introduction on using [Kubernetes with R is published at this blog post](https://code.markedmondson.me/r-on-kubernetes-serverless-shiny-r-apis-and-scheduled-scripts/).

>>>>

The cloud is the natural environment of containers, and subsequently containers are the go-to mechanism to deploy R server applications.
More and more continuous integration (CI) and continuous delivery (CD) services also use containers, opening up new options for use.
The controlled nature of containers, i.e., the possibility to define the software environment very well, even on remote machines, is crucial here, for example to match test or build environments with production environments.

As a first example, \CRANpkg{Shiny} is the most popular package for creating interactive online dashboards with R and it enables users with very diverse backgrounds to create stable and user friendly web applications.
The ShinyProxy ([https://www.shinyproxy.io/](https://www.shinyproxy.io/)) is an open source tool to deploy Shiny apps in an enterprise context.
They feature single sign-on, but also in scientific use cases \citep[e.g., ][]{savini_epiexplorer_2019,glouzon_structurexplor_2017}.
ShinyProxy uses Docker containers to isolate user sessions and to achieve scalability for multi-user scenarious with multiple apps.
ShinyProxy itself is written in Java to accomodate corporate requirements and may itself run in a container for stability and availability.
The tool is build on ContainerProxy ([https://www.containerproxy.io/](https://www.containerproxy.io/)), which provides similar features for executign long-running R jobs or interactive R sessions.
The started containers can run on a regular Docker host but also in clusters.
- `RSelenium`
- [`googleComputeEngineR`](https://cloudyr.github.io/googleComputeEngineR/) (function `gce_vm_template()`)
  - To enable quick deployments of key R services such as RStudio and Shiny onto cloud virtual machines (VMs), this package utilises Dockerfiles to move the labour of setting up those services from the user to a premade Docker image. For example, by specifying the template `template="rstudio"` in `gce_vm_template()/gce_vm()` an up to date RStudio Service image is launched.  Specifying `template="rstudio-gpu"` will launch an RStudio Server image with a GPU attached, etc.  
- [`analogsea`](https://github.com/sckott/analogsea) (digital ocean R client)
- [`plumber`](https://www.rplumber.io/docs/hosting.html#docker)
- [production deployment of neural networks](https://github.com/tmobile/r-tensorflow-api) [@jnolis, @nolistic]
- Kubernetes - A popular platform for managing Docker containers is [Kubernetes](https://kubernetes.io/), which is used for a wide variety of containerized applications. It may be your organisation has a Kubernetes cluster already for other applications. Docker containers are used within Kubernetes clusters to hold native code, for which Kubernetes creates a framework around network connections and scaling of resources up and down. An introduction on using [Kubernetes with R is published at this blog post](https://code.markedmondson.me/r-on-kubernetes-serverless-shiny-r-apis-and-scheduled-scripts/).
